Child care situation of working mothers in Ghana 1998

### 2022-04-03 inputs/data/datasheet_template.Rmd
Fix cross-reference issues

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Pascal Lee Slew
  - Yunkyung Park
thanks: "Code and data are available at: LINK."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references_datasheet.bib
---

>>>>

---
title: "Datasheet"
author: 
  - Pascal Lee Slew
  - Yunkyung Park
thanks: "Code and data are available at: LINK."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references_datasheet.bib
---

### 2022-04-03 outputs/paper.Rmd
small changes
Fix cross-reference issues

---
title: "Childcare while their mom is working"
author: 
  - Pascal Lee Slew
  - Yunkyung Park
thanks: "Code and data are available at: https://github.com/Pascal-304/dhs_analysis."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "Working mothers are often faced with the conflict of responsibility towards their children and the role they play at work. The Ghana Demographic and Health Survey (GDHS) forms a part of a global initiative to collect data on family, fertility, and child health. In this paper, we used the 1998 GDHS and focused on the child care and working mothers aspect. Geographics and other aspects such as education are used to predict child care preference. We found that families living in Greater Accra are more likely to send their children to school and the majority of working mothers look after their children by themselves. The analysis of the child care and working mothers data provides insight into current trends and has significant implications for public policy and program decisions."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

@@

The rest of the paper is divided into 4 sections. Section \@ref(data) explains the data source, the survey methodology, and some of its key features, strengths, and weaknesses. Section \@ref(results) relays the findings through graphs. Section @\ref(discussion) discusses in more detail what was found and some limitations of what we did and Section \@ref(appendix) contains a datasheet for the dataset we used.

@@

Figure @\ref(fig:region) shows the number of employed mothers in the different administrative regions. There were more working mothers in Greater Accra and Ashanti while Upper West had the least number of working mothers. The reason might be because the number of people living in the different administrative regions is different, therefore, the sample size differed from one region to another. Greater Accra is the most urbanized region which implies more work opportunities and therefore, a larger population would be concentrated there.

@@

Figure @\ref(fig:areachildcare) shows the Ghanese families' caretaking preferences in both urban and rural areas. The preferred caretaking method in both urban and rural areas is the working mothers looking after their children by themselves. The next preferred method in both areas would be to let the children be looked after by relatives. Other notable observations would be that families living in urban areas tend to put their children in school and in rural areas, families let the older female child care for the under six years old child much more than in urban areas.

@@

>>>>

---
title: "Child care situation of working mothers in Ghana 1998"
author: 
  - Pascal Lee Slew
  - Yunkyung Park
thanks: "Code and data are available at: https://github.com/Pascal-304/dhs_analysis."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "Working mothers are often faced with the conflict of responsibility towards their children and the role they play at work. The Ghana Demographic and Health Survey (GDHS) forms a part of a global initiative to collect data on family, fertility, and child health. In this paper, we used the 1998 GDHS and focused on the child care and working mothers aspect. Geographics and other aspects such as education are used to predict child care preference. We found that families living in Greater Accra are more likely to send their children to school and the majority of working mothers look after their children by themselves. The analysis of the child care and working mothers data provides insight into current trends and has significant implications for public policy and program decisions."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

@@

The rest of the paper is divided into 4 sections. Section \@ref(data) explains the data source, the survey methodology, and some of its key features, strengths, and weaknesses. Section \@ref(results) relays the findings through graphs. Section \@ref(discussion) discusses in more detail what was found and some limitations of what we did and Section \@ref(appendix) contains a datasheet for the dataset we used.

@@

Figure \@ref(fig:region) shows the number of employed mothers in the different administrative regions. There were more working mothers in Greater Accra and Ashanti while Upper West had the least number of working mothers. The reason might be because the number of people living in the different administrative regions is different, therefore, the sample size differed from one region to another. Greater Accra is the most urbanized region which implies more work opportunities and therefore, a larger population would be concentrated there.

@@

Figure \@ref(fig:areachildcare) shows the Ghanese families' caretaking preferences in both urban and rural areas. The preferred caretaking method in both urban and rural areas is the working mothers looking after their children by themselves. The next preferred method in both areas would be to let the children be looked after by relatives. Other notable observations would be that families living in urban areas tend to put their children in school and in rural areas, families let the older female child care for the under six years old child much more than in urban areas.

@@

# Appendix
